The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-11-18 papers/pair-correlation/paper.tex
modified paper Tested on node33. Took .

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\refnote}{\red{[ref]}}

@@

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...

@@

The demand that our solution is correct in the homogeneous limit forms
the basis of the derivation of our radial distribtuion's function
form. We use the well known and very successful Carnahan Starling
equation to calculated $g_{\sigma}$ and then simple monte-carlo
simulations to calculate values of the homogeneous radial distribution
function at varying distance perameter $r$ (Our previously published
$g_{\sigma}$ approaches the Carnahan Starling version in the
homogeneous limit and it's simplest to use an analytical expression
for this calculation).  We then construct our radial distribution
function that has the form of an expansion of powers of $h_{\sigma} =
g_{\sigma}-1$ and perform a least squares fit to the monte-carlo
solution to find the needed constant perameters.  The function is
constructed in such a way as to appoach $g_{\sigma}$ in the limit of
contact distance between the particles.  After this process we have a
radial distribution function that is dependent only on $g_{\sigma}$
and that gives the correct solution in the homogeneous and contact
distance limit.

@@

>>>>

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\refnote}{\red{[ref]}}

@@

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\green{Jeff:} \emph{#1}]}}

@@

We construct our function's form in terms of an expansion of powers of
$h_{\sigma} = g_{\sigma}-1$, ensuring that it approaches $g_{\sigma}$
in the contact distance limit, leaving our function with tunable
constant perameters.  We run a simple monte-carlo simulations to
calculate values of the homogeneous radial distribution function at
varying distance perameter $r$.  We then tune our function's constant
perameters by matching our function's results against the monte-carlo
data, using a least squares fit method.  During this process it is
simplest to use an analytic expression for $g_{\sigma}$ in our
function and so we use the well known and very successful Carnahan
Starling equation to calculate $g_{\sigma}$.  This is appropriate
since that our published $g_{\sigma}$ approaches the Carnahan Starling
version in the homogeneous limit and it's this limit, along with the
contact limit, that we would like our constructed radial distribution
function to get right.  After this process we have an appropriate
radial distribution function that is dependent only on $r$ and
$g_{\sigma}$.

@@

\jeffsays{I'm confused by this next part.  Are we just saying that
  instead of using our published $g_{\sigma}$ we could have used a
  Carnahan Starling derived $g_{\sigma}$? Don't understand why that
  would add an unnecessary step in using g(r).}
